Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)

### 2015-10-17 paper.tex
arrumado titulo, finalmente

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Stability of interaction networks]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}
%
%\author{Vilson V. da Silva Jr.}
%\homepage{http://automata.cc/}
%\email{vilson@void.cc}
%\altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Ricardo Fabbri}
\homepage{http://www.lems.brown.edu/~rfabbri/}
\email{rfabbri@iprj.uerj.br}
\altaffiliation{
	Instituto Polit\'ecnico, Universidade Estadual do Rio de Janeiro (IPRJ)
}%Lines break automatically or can be forced with \\

>>>>

%\title[Evolution of interaction networks]{On the evolution of interaction networks: primitive typology of vertex, prominence of measures and activity statistics}% Force line breaks with \\
%\title[Evolution of interaction networks]{On the evolution of interaction networks: a primitive typology of vertex}% Force line breaks with \\
%\title[Stability of interaction networks]{Stability in human interaction networks: sector relative sizes, prominence of topological measures and time activity statistics.}% Force line breaks with \\
%\title[Stability in human interaction networks]{Sector relative sizes and topological metrics time stability in human interaction networks}% Force line breaks with \\
\title[Stability of interaction networks]{Temporal stability in human interaction networks: sector sizes, topological prominence and activity along different timescales}% Force line breaks with \\
\author{Renato Fabbri}%
\homepage{http://ifsc.usp.br/~fabbri/}
\email{fabbri@usp.br}
\affiliation{ 
	S\~ao Carlos Institute of Physics, University of S\~ao Paulo (IFSC/USP),
	PO Box 369, 13560-970, S\~ao Carlos, SP, Brazil %\\This line break forced with \textbackslash\textbackslash
}
%
%\author{Vilson V. da Silva Jr.}
%\homepage{http://automata.cc/}
%\email{vilson@void.cc}
%\altaffiliation[Also at ]{IFSC-USP}%Lines break automatically or can be forced with \\
%
\author{Ricardo Fabbri}
\homepage{http://www.lems.brown.edu/~rfabbri/}
\email{rfabbri@iprj.uerj.br}
\altaffiliation{
	Instituto Polit\'ecnico, Universidade Estadual do Rio de Janeiro (IPRJ)
}%Lines break automatically or can be forced with \\

### 2015-10-17 supportingInformation.tex
arrumado titulo, finalmente

Loadings for 14 topological metrics in the first three principal components are given for LAD, LAU, MET, CPP, list..
The clustering coefficient $cc$ appears as the first metric in the tables, followed by 7 centrality metrics and 6 symmetry-related metrics.
The centrality metrics, including degrees, strengths and betweenness centrality, are most important for the first principal component, while the second component is predominantly symmetry metrics.
The clustering coefficient is only relevant for the third principal component, coupled with standard deviations of strengths and degrees.
The three components hold in average $\approx 80.36\%$ of the variance.
In the PCA measures of the CPP list, in the last table, this general pattern is depicted in {\bf boldface}.
Further details are given in Sections~\ref{measures} and~\ref{prevalence} of the main document~\cite{tpaper}.

@@

\FloatBarrier
\section{Stability in networks from Twitter, Facebook, Participabr}\label{si:ext}
To ease hypothesizing about the generality of the reported stability of human interaction networks,
this section presents the topological analysis of
networks from Twitter, Facebook and Participabr.
Selected networks are summarized in
Table~\ref{tab:E}. Their Erd\"os sector relative sizes are given in Table~\ref{tab:secE}. PCA formations are given in
Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. The friendship networks considered are undirected and unweighted, therefore all measurements of strength, in- and out- centralities, asymmetry and disequilibrium have little or no meaning, which is why F1, F2, F3, F4 and F5 are only present in Table~\ref{tab:pcaE1F}.
The most important results from this analysis are:

@@

\begin{table*}[!h]
	\caption{Selected networks from three social platforms: Facebook, Twitter and Participabr.
	Both friendship and interaction networks were observed, yielding undirected and directed networks, respectively.
The number of agents $N$ and the number of edges $z$ are given on the last columns.
The acronyms, one for each network, are used throughout Tables~\ref{tab:secE},~\ref{tab:pcaE1I},~\ref{tab:pcaE1F},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. All the data were collected in 2013 and 2014 within the anthropological physics framework~\cite{anPhy}.}
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c | }\hline
	acronym & provenance & edge & directed & description & $N$ & $z$ \\ \hline\hline
	\input{tables/tabExtra}
\hline
\end{tabular}
\end{center}
\label{tab:E}
\end{table*}

\begin{table*}[!h]
	\caption{
	Percentage of agents in each Erd\"os sector in the friendship and interaction human networks of Table~\ref{tab:E}. The ratios found in email networks are preserved. I1 and I4 are outliers, probably because they should be better characterized as a superposition of networks, rather than one coherent network. The degree was used for establishing the sectors.
	}
\begin{center}
\begin{tabular}{| l | c | c | c |}\hline
	 & periphery & intermediary & hubs \\ \hline\hline
	\input{tables/tabSectorsExtra}
\hline
\end{tabular}
\end{center}
\label{tab:secE}
\end{table*}

>>>>

Loadings for 14 topological metrics in the first three principal components are given for LAD, LAU, MET, CPP, list..
The clustering coefficient $cc$ appears as the first metric in the tables, followed by 7 centrality metrics ($k$, $k^{in}$, $k^{out}$, $s$, $s^{in}$, $s^{ou}$, $bt$) and 6 symmetry-related metrics ($asy$, $\mu^{asy}$, $\sigma^{asy}$, $dis$, $\mu^{dis}$ and $\sigma^{dis}$).
The centrality metrics are most important for the first principal component, while the second component is predominantly the result of symmetry metrics.
The clustering coefficient is only relevant for the third principal component, coupled with standard deviations of asymmetry $\sigma^{asy}$ and disequilibrium $\sigma^{dis}$.
The three components sum up to $\approx90\%$ of the variance.
In the PCA measures of the CPP list, the last table of these PCA-related tables, this general pattern is depicted in {\bf boldface}.
Further details are given in Sections~\ref{measures} and~\ref{prevalence} of the main document~\cite{tpaper}.

@@

\FloatBarrier
\section{Stability in networks from Twitter, Facebook, Participabr}\label{si:ext}
To ease hypothesizing about the generality of the reported stability of human interaction networks,
this section presents the topological analysis of
networks from Twitter, Facebook and Participabr.
Selected networks are summarized in
Table~\ref{tab:E}. Their Erd\"os sector relative sizes are given in Table~\ref{tab:secE}. The formation of Principal components
are given in
Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. The friendship networks considered are undirected and unweighted, therefore all measurements of strength, in- and out- centralities, asymmetry and disequilibrium have little or no meaning, which is why F1, F2, F3, F4 and F5 are only present in Table~\ref{tab:pcaE1F}.
The most important results from this analysis are:

@@

\begin{table*}[!h]
	\caption{Selected networks from three social platforms: Facebook, Twitter and Participabr.
	Both friendship and interaction networks were observed, yielding undirected and directed networks, respectively.
The number of agents $N$ and the number of edges $z$ are given on the last columns.
The acronyms, one for each network, are used throughout Tables~\ref{tab:secE},~\ref{tab:pcaE1I},~\ref{tab:pcaE1F},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. All the data were collected in 2013 and 2014 within the anthropological physics framework~\cite{anPhy}.}
\begin{center}
\begin{tabular}{| l || c | c | c | c | c | c | }\hline
	acronym & provenance & edge & directed & description & $N$ & $z$ \\ \hline
	\input{tables/tabExtra}
\hline
\end{tabular}
\end{center}
\label{tab:E}
\end{table*}

\begin{table*}[!h]
	\caption{
	Percentage of agents in each Erd\"os sector in the friendship and interaction human networks of Table~\ref{tab:E}. The ratios found in email networks are preserved. I1 and I4 are outliers, probably because they should be better characterized as a superposition of networks, rather than one coherent network. The degree was used for establishing the sectors.
	}
\begin{center}
\begin{tabular}{| l || c | c | c |}\hline
	 & periphery & intermediary & hubs \\ \hline
	\input{tables/tabSectorsExtra}
\hline
\end{tabular}
\end{center}
\label{tab:secE}
\end{table*}
